Near Optimal Behavior via Approximate State Abstraction

### 2016-05-26 paper/abstraction_notation.tex
final pass

%Lihong Section
\section{Abstraction Notation}
We build upon the notation used by \citet{li2006towards}, who introduced a unifying theoretical framework for state abstraction in \acp{MDP} and sequential decision making.

@@

The abstract reward function and abstract transition dynamics for each abstract state are a weighted combination of the rewards and transitions for each ground state in the partition. We make no assumptions about the weighting scheme, except that for each abstract state, the weighting is a convex combination across all ground states.

@@

\bdefn{$\omega(s)$}
We refer to the weight associated with a ground state, $s \in \mathcal{S}_G$ by $\omega(s)$. The only restriction placed on the weighting scheme is that it induces a probability distribution on the ground states of each abstract state:
\begin{equation}
\forall s \in \mcS_G \left(\sum_{s \in G(s)} \omega(s)\right) = 1 \textrm{ and }\hspace{6mm}  \omega(s) \in [0,1].
\end{equation}
\edefn

% Reward
\bdefn{$\mcR_A$}
The abstract reward function $\mathcal{R}_A(s,a)$ is a weighted sum of the rewards of each of the ground states that map to the same abstract state:
\begin{equation}
\mathcal{R}_A(s,a) = \sum_{g \in G(s)} \mathcal{R}_G(g,a) \omega(g) .
\end{equation}
\edefn

% Transition
\bdefn{$\mcT_A$}
The abstract transition function $\mathcal{T}_A(s,a,s')$ is a weighted sum of the transitions of each of the ground states that map to the same abstract state:
\begin{equation}
\mathcal{T}_A(s,a,s') = \sum_{g \in G(s)} \sum_{g' \in G(s')} \mathcal{T}_G(g,a,g') \omega(g).
\end{equation}
\edefn

>>>>

%Lihong Section
\section{Abstraction Notation}
We build upon the notation used by \citet{li2006towards}, who introduced a unifying theoretical framework for state abstraction in \acp{MDP}.

@@

The abstract reward function and abstract transition dynamics for each abstract state are a weighted combination of the rewards and transitions for each ground state in the abstract state.

@@

\bdefn{$\omega(s)$}
We refer to the weight associated with a ground state, $s \in \mathcal{S}_G$ by $\omega(s)$. The only restriction placed on the weighting scheme is that it induces a probability distribution on the ground states of each abstract state:
\begin{equation}
\forall s \in \mcS_G \left(\sum_{s \in G(s)} \omega(s)\right) = 1 \hspace{3mm} \textrm{ AND }\hspace{3mm}  \omega(s) \in [0,1].
\end{equation}
\edefn

% Reward
\bdefn{$\mcR_A$}
The abstract reward function $\mathcal{R}_A: \mathcal{S}_A \times \mathcal{A} \mapsto [0,1]$ is a weighted sum of the rewards of each of the ground states that map to the same abstract state:
\begin{equation}
\mathcal{R}_A(s,a) = \sum_{g \in G(s)} \mathcal{R}_G(g,a) \omega(g) .
\end{equation}
\edefn

% Transition
\bdefn{$\mcT_A$}
The abstract transition function $\mathcal{T}_A: \mathcal{S}_A \times \mathcal{A} \times \mathcal{S}_A \mapsto [0,1]$ is a weighted sum of the transitions of each of the ground states that map to the same abstract state:
\begin{equation}
\mathcal{T}_A(s,a,s') = \sum_{g \in G(s)} \sum_{g' \in G(s')} \mathcal{T}_G(g,a,g') \omega(g).
\end{equation}
\edefn

### 2016-05-26 paper/introduction.tex
added authorship comment
final pass

Abstraction plays a fundamental role in learning. Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant. Consequently, agents are able to solve considerably more complex problems than they would be able to without the use of abstraction. However, \textit{exact abstractions}, which treat only fully-identical situations as equivalent, require complete knowledge that is often computationally intractable to obtain. Furthermore, often no two situations are identical, so exact abstractions are often ineffective. To overcome these issues, we investigate \textit{approximate abstractions} that enable agents to treat sufficiently similar situations as identical. This work characterizes the impact of equating ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}. The remainder of our introduction contextualizes these intuitions in \acp{MDP}.

% Abstraction is a good idea b/c MDP has poly comp comp and samp comp in S, but S grows fast.
Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{papadimitriou1987complexity,littman1995complexity}. Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}. Although polynomial runtime or sample complexity may seem like a reasonable constraint, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain, a result of Bellman's curse of dimensionality. Thus, solutions polynomial in state space size are often ineffective for sufficiently complex tasks. For instance, a robot involved in a pick-and-place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider grows exponentially with the number of objects with which it is working \cite{abel2015goal}.

@@

% Thesis: Approximate abstraction for three reasons.
The thesis of this work is that performing approximate abstraction in \acp{MDP} by relaxing the state-aggregation criteria from equality of quantities to $\varepsilon$-closeness maintains bounded error in the resulting behavior while offering three benefits. First, approximate abstractions employ the sort of knowledge that we expect a planning or learning algorithm to compute without fully solving the \ac{MDP}. In contrast, exact abstractions often require solving for optimal behavior, thereby defeating the purpose of abstraction. Second, because of their relaxed criteria, approximate abstractions can achieve greater degrees of compression than exact abstractions. This difference is particularly important in environments where no two states are identical. Third, because the state-aggregation criteria are relaxed to near equality, approximate abstractions are able to tune the aggressiveness of abstraction by adjusting what they consider sufficiently similar states.

>>>>

Abstraction plays a fundamental role in learning. Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant. Consequently, agents are able to solve considerably more complex problems than they would be able to without the use of abstraction. However, \textit{exact abstractions}, which treat only fully-identical situations as equivalent, require complete knowledge that is computationally intractable to obtain. Furthermore, often no two situations are identical, so exact abstractions are often ineffective. To overcome these issues, we investigate \textit{approximate abstractions} that enable agents to treat sufficiently similar situations as identical. This work characterizes the impact of equating ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}. The remainder of our introduction contextualizes these intuitions in \acp{MDP}.

% Abstraction is a good idea b/c MDP has poly comp comp and samp comp in S, but S grows fast.
Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{papadimitriou1987complexity,littman1995complexity}. Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}. Although polynomial runtime or sample complexity may seem like a reasonable constraint, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain - a result of Bellman's curse of dimensionality. Thus, solutions polynomial in state space size are often ineffective for sufficiently complex tasks. For instance, a robot involved in a pick-and-place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider grows exponentially with the number of objects with which it is working \cite{abel2015goal}.

@@

\footnotetext[2]{The first two authors contributed equally.}
\renewcommand*{\thefootnote}{\arabic{footnote}}

% Thesis: Approximate abstraction for three reasons.
The thesis of this work is that performing approximate abstraction in \acp{MDP} by relaxing the state-aggregation criteria from equality to similarity achieves polynomially bounded error in the resulting behavior while offering three benefits. First, approximate abstractions employ the sort of knowledge that we expect a planning or learning algorithm to compute without fully solving the \ac{MDP}. In contrast, exact abstractions often require solving for optimal behavior, thereby defeating the purpose of abstraction. Second, because of their relaxed criteria, approximate abstractions can achieve greater degrees of compression than exact abstractions. This difference is particularly important in environments where no two states are identical. Third, because the state-aggregation criteria are relaxed to near equality, approximate abstractions are able to tune the aggressiveness of abstraction by adjusting what they consider sufficiently similar states.

### 2016-05-26 paper/mdp_background.tex
final pass

The objective of an agent is to solve for the policy that maximizes its expected discounted reward from any state, denoted $\pi^*$. We denote the expected discounted reward for following policy $\pi$ from state $s$ as the value of the state under that policy, $V^\pi(s)$. We similarly denote the expected discounted reward for taking action $a \in \mathcal{A}$ and then following policy $\pi$ from state $s$ forever after as $Q^\pi(s,a)$, defined by the Bellman Equation as:
\begin{equation}
Q^\pi(s,a) = \mathcal{R}(s,a) + \gamma \sum_{s'} \mathcal{T}(s,a,s') Q^\pi(s',\pi(s')).
\end{equation}
We let \textsc{RMax} denote the maximum reward (which is 1), and \textsc{QMax} denote the maximum Q value, which is $\frac{\textsc{RMax}}{1-\gamma}$.

>>>>

The objective of an agent is to solve for the policy that maximizes its expected discounted reward from any state, denoted $\pi^*$. We denote the expected discounted reward for following policy $\pi$ from state $s$ as the value of the state under that policy, $V^\pi(s)$. We similarly denote the expected discounted reward for taking action $a \in \mathcal{A}$ and then following policy $\pi$ from state $s$ forever after as $Q^\pi(s,a)$, defined by the Bellman Equation as:
\begin{equation}
Q^\pi(s,a) = \mathcal{R}(s,a) + \gamma \sum_{s'} \mathcal{T}(s,a,s') Q^\pi(s',\pi(s')).
\end{equation}
We let \textsc{RMax} denote the maximum reward (which is 1), and \textsc{QMax} denote the maximum $Q$ value, which is $\frac{\textsc{RMax}}{1-\gamma}$.

### 2016-05-26 paper/related_work.tex
adding changes for camera ready: ferns added, lemma 3 and 4 beefed up, vareps added to functions
final pass

\subsection{Approximate State Abstraction}
\citet{dean1997model} investigated partitioning an \ac{MDP}'s state space into $\varepsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\varepsilon$ of each other. They develop an algorithm called Interval Value Iteration (IVI) that converges to the correct bounds on a family of abstract MDPs called Bounded \acp{MDP}. Several approaches build on the notion of $\varepsilon$-homogeneity. \citet{even2003approximate} analyzed different distance metrics used in the process of identifying $\varepsilon$-homogenous partitions. \citet{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $\mcT$ and $\mcR$ provided by UCRL~\cite{auer2009near}.

@@

\citet{li2006towards} developed a framework for exact state abstraction in \acp{MDP}. In particular, the authors defined five types of state-aggregation functions, inspired by existing methods for state aggregation in \acp{MDP}. We generalize two of these five types, $\phi_{Q^*}$ and $\phi_{\text{model}}$, to the approximate abstraction case. Our generalizations are equivalent to theirs when exact criteria are used. Additionally, when exact criteria are used our bounds indicate that no value is lost, which is one of core results of \citet{li2006towards}.

>>>>

\subsection{Approximate State Abstraction}
\citet{dean1997model} leverage the notion of {\it bisimulation} to investigate partitioning an \ac{MDP}'s state space into clusters of states whose transition model and reward function are within $\varepsilon$ of each other. They develop an algorithm called Interval Value Iteration (IVI) that converges to the correct bounds on a family of abstract MDPs called Bounded \acp{MDP}.

Several approaches build on \citet{dean1997model}. \citet{ferns2004metrics,ferns2006methods} investigated state similarity metrics for \acp{MDP}; they bounded the value difference of ground states and abstract states for several bisimulation metrics that induce an abstract MDP. This differs from our work which develops a theory of abstraction that bounds the suboptimality of applying the optimal policy of an abstract MDP to its ground MDP, covering four types of state abstraction, one of which closely parallels bisimulation. \citet{even2003approximate} analyzed different distance metrics used in identifying state space partitions subject to $\varepsilon$-similarity. \citet{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $\mcT$ and $\mcR$ provided by UCRL~\cite{auer2009near}.

@@

\citet{li2006towards} developed a framework for exact state abstraction in \acp{MDP}. In particular, the authors defined five types of state-aggregation functions, inspired by existing methods for state aggregation in \acp{MDP}. We generalize two of these five types, $\phi_{Q^*}$ and $\phi_{\text{model}}$, to the approximate abstraction case. Our generalizations are equivalent to theirs when exact criteria are used (i.e. $\varepsilon = 0$). Additionally, when exact criteria are used our bounds indicate that no value is lost, which is one of core results of \citet{li2006towards}.

### 2016-05-26 paper/theory_results.tex
final pass

\label{sec:theory_results}
% Intro to approx state abstraction results.
Here, we introduce our formal analysis of approximate state abstraction, including results bounding the error associated with these abstraction methods. In particular, we demonstrate that abstractions based on approximate $Q^*$ similarity (\ref{sec:Q*}), approximate model similarity (\ref{sec:model}), and approximate similarity between distributions over $Q^*$, for both Boltzmann (\ref{sec:boltz}) and multinomial (\ref{sec:mult}) distributions, induce abstract \acp{MDP} for which the optimal policy has bounded error in the ground MDP.

@@

We now introduce the main result of the paper.

@@

We prove this theorem in the following sections by proving bounds on the error of each individual approximate state-aggregation function type.

@@

% Q* Lemma -- lemma 1
We consider an approximate version of \citet{li2006towards}'s $\phi_Q^*$,. In our abstraction, states are aggregated together when their optimal $Q$-values are within $\varepsilon$.
\bdefn{$\epQ$}
An approximate $Q$ function has the same form as Equation~\ref{eq:phi_f}:
\vspace{-1mm}%vspace for more space
\begin{equation}
\ep_{Q^*,\varepsilon}(s_1) = \ep_{Q^*,\varepsilon}(s_2) \rightarrow \forall_a \left|Q_G^*(s_1, a) - Q_G^*(s_2, a)\right| \leq \varepsilon.
\end{equation}
\edefn

@@

Consider a non-Markovian decision process of the same form as an \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of $M_G$. Thus,
\begin{align*}
\mathcal{S}_T &= \begin{cases}
\mathcal{S}_G,& \text{if } T = 0, \\
\mathcal{S}_A,& \text{o/w}
\end{cases}\\
\end{align*}
\begin{align*}
\mathcal{R}_T(s,a) &= \begin{cases}
\mathcal{R}_G(s,a),& \text{if } T = 0, \\
\mathcal{R}_A(s, a),& \text{o/w}
\end{cases}\\
\end{align*}
\begin{align*}
\mcT_T(s,a,s') &= \begin{cases}
\mcT_G(s,a,s'),& \text{if }T = 0, \\
\underset{{g \in G(s)}}{\sum}\left[\omega(g)\mcT_G(g, a, s')\right],& \text{if } T = 1, \\
\mcT_A(s,a,s'),& \text{o/w}
\end{cases}\\
\end{align*}
The $Q$-value of state $s$ in $\mathcal{S}_T$ for action $a$ is:
\begin{equation}
Q_T(s, a) = 
\begin{cases}
	   Q_G(s, a), &  \text{if } T=0,\\
	   \underset{g \in G(s)}{\sum} \left[ \omega(g)Q_G(g,a) \right], & \text{if } T = 1,\\
	   \mathcal{R}_A(s,a) + \sigma_{T-1}(s,a), &\text{o/w},
\end{cases}
\end{equation}
where
\begin{equation*}
\sigma_{T-1}(s,a) = \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(s,a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a').
\end{equation*}
We proceed by induction on $T$ to show that:
\begin{equation}
\label{eq:clm1Induct}
\forall_{T, s_G \in \mathcal{S}_G, a} |Q_T(s_T, a) - Q_G(s_G, a) | \leq \sum_{t=0}^{T-1} \varepsilon \gamma^{t},
\end{equation}
where $s_T = s_G$ if $T=0$ and $s_T = \epQ(s_G)$ otherwise.

@@

Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$, and fixed but arbitrary action $a$.
Since $T > 1$, $s_T$ is $\epQ(s_G)$.
By definition of $Q_{T}(s_T, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:
\begin{multline*}
Q_T(s_T, a) = \sum_{g \in G(s_T)}\omega(g)\ \times \\ 
 \left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right].
\end{multline*}
Applying our inductive hypothesis yields:
\begin{multline*}
Q_T(s_T, a) \leq \sum_{g \in G(s_T)}\omega(g) \times \biggl[ R_G(g,a)\ + \\ \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \varepsilon \gamma^t) \biggr].
\end{multline*}
%&\leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \sum_{g \in X(s_A)}\omega(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
%Then,
%\begin{equation*}
%Q_T(s_T, a) \leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \sum_{g \in G(s_T)}\left[ \omega(g)\ Q_G(g,a)\right].
%\end{equation*}
Since all aggregated states have $Q$-values within $\varepsilon$ of one another:
\begin{align*}
Q_T(s_T, a) \leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \varepsilon + Q_G(s_G, a). \\
%\therefore\ \left| Q_{T}(s_T, a) - Q_G(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\varepsilon \gamma^t
\end{align*}
$s_G$ is arbitrary so we conclude Equation \ref{eq:clm1Induct}. As $T \rightarrow \infty$, $\sum_{t=0}^{T-1} \varepsilon \gamma^t \rightarrow \frac{\varepsilon}{1-\gamma}$ by the sum of infinite geometric series and $Q_T \rightarrow Q_A$. Thus, Equation \ref{eq:clm1Induct} gives Claim \ref{clm:closeQs}.

@@

Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$ and its corresponding abstract state $s_A=\epQ(s_G)$.
Let $a^*_G$ stand for the optimal action in $s_G$, and $a^*_A$ stand for the optimal action in $s_A$:
\begin{align*}
a^*_G = \argmin Q_G(s_G, a), \hspace{4mm}
a^*_A = \argmin Q_A(s_A, a).
\end{align*}
The optimal action in the abstract MDP has a $Q$-value in the ground MDP that is nearly optimal:
\begin{equation}
\label{eq:Q*Claim2}
V_G(s_G) \leq Q_G(s_G, a^*_A) + \frac{2\varepsilon}{1-\gamma}.
\end{equation}
\end{clm}

By Claim~\ref{clm:closeQs},
\begin{align}
&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_A, a^*_G) + \frac{\varepsilon}{1-\gamma}.
\label{eq:Q*OptActionResult}
\end{align}

By the definition of $a^*_A$, we know that 
\begin{align}
Q_A(s_A, a^*_G) + \frac{\varepsilon}{1-\gamma} \leq Q_A(s_A, a^*_A) + \frac{\varepsilon}{1-\gamma}.
\end{align}

Lastly, again by Claim~\ref{clm:closeQs}, we know
\begin{align}
Q_A(s_A, a^*_A) + \frac{\varepsilon}{1-\gamma} \leq Q_G(s_g, a^*_A) + \frac{2\varepsilon}{1-\gamma}.
\end{align}
Therefore, Equation~\ref{eq:Q*Claim2} follows.

>>>>

\label{sec:theory_results}
% Intro to approx state abstraction results.
Here, we introduce our formal analysis of approximate state abstraction, including results bounding the error associated with these abstraction methods. In particular, we demonstrate that abstractions based on approximate $Q^*$ similarity (\ref{sec:Q*}), approximate model similarity (\ref{sec:model}), and approximate similarity between distributions over $Q^*$, for both Boltzmann (\ref{sec:boltz}) and multinomial (\ref{sec:mult}) distributions induce abstract \acp{MDP} for which the optimal policy has bounded error in the ground MDP.

@@

We now introduce our main result.

@@

We prove this theorem in the following sections by proving polynomial bounds on the error of each individual approximate state-aggregation function type.

@@

% Q* Lemma -- lemma 1
We consider an approximate version of \citet{li2006towards}'s $\phi_{Q^*}$. In our abstraction, states are aggregated together when their optimal $Q$-values are within $\varepsilon$.
\bdefn{$\epQ$}
An approximate $Q$ function abstraction has the same form as Equation~\ref{eq:phi_f}:
\vspace{-1mm}%vspace for more space
\begin{equation}
\ep_{Q^*,\varepsilon}(s_1) = \ep_{Q^*,\varepsilon}(s_2) \rightarrow \forall_a \left|Q_G^*(s_1, a) - Q_G^*(s_2, a)\right| \leq \varepsilon.
\end{equation}
\edefn

@@

Consider a non-Markovian decision process of the same form as an \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of $M_G$. Thus,
\begin{align*}
\mathcal{S}_T &= \begin{cases}
\mathcal{S}_G,& \text{if } T = 0, \\
\mathcal{S}_A,& \text{o/w}
\end{cases}\\
\end{align*}
\begin{align*}
\mathcal{R}_T(s,a) &= \begin{cases}
\mathcal{R}_G(s,a),& \text{if } T = 0, \\
\mathcal{R}_A(s, a),& \text{o/w}
\end{cases}\\
\mcT_T(s,a,s') &= \begin{cases}
\mcT_G(s,a,s'),& \text{if }T = 0, \\
\underset{{g \in G(s)}}{\sum}\left[\omega(g)\mcT_G(g, a, s')\right],& \text{if } T = 1, \\
\mcT_A(s,a,s'),& \text{o/w}
\end{cases}
\end{align*}
The $Q$-value of state $s$ in $\mathcal{S}_T$ for action $a$ is:
\begin{equation}
Q_T(s, a) = 
\begin{cases}
	   Q_G(s, a), &  \text{if } T=0,\\
	   \underset{g \in G(s)}{\sum} \left[ \omega(g)Q_G(g,a) \right], & \text{if } T = 1,\\
	   \mathcal{R}_A(s,a) + \sigma_{T-1}(s,a), &\text{o/w},
\end{cases}
\end{equation}
where:
\begin{equation*}
\sigma_{T-1}(s,a) = \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(s,a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a').
\end{equation*}
We proceed by induction on $T$ to show that:
\begin{equation}
\label{eq:clm1Induct}
\forall_{T, s_G \in \mathcal{S}_G, a} |Q_T(s_T, a) - Q_G(s_G, a) | \leq \sum_{t=0}^{T-1} \varepsilon \gamma^{t},
\end{equation}
where $s_T = s_G$ if $T=0$ and $s_T = \epQ(s_G)$ otherwise.

@@

Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$, and fixed but arbitrary action $a$.
Since $T > 1$, $s_T$ is $\epQ(s_G)$.
By definition of $Q_{T}(s_T, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:
\begin{multline*}
Q_T(s_T, a) = \sum_{g \in G(s_T)}\omega(g)\ \times \\ 
 \left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right].
\end{multline*}
Applying our inductive hypothesis yields:
\begin{multline*}
Q_T(s_T, a) \leq \sum_{g \in G(s_T)}\omega(g) \times \biggl[ R_G(g,a)\ + \\ \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \varepsilon \gamma^t) \biggr].
\end{multline*}
%&\leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \sum_{g \in X(s_A)}\omega(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
%Then,
%\begin{equation*}
%Q_T(s_T, a) \leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \sum_{g \in G(s_T)}\left[ \omega(g)\ Q_G(g,a)\right].
%\end{equation*}
Since all aggregated states have $Q$-values within $\varepsilon$ of one another:
\begin{align*}
Q_T(s_T, a) \leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \varepsilon + Q_G(s_G, a).
%\therefore\ \left| Q_{T}(s_T, a) - Q_G(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\varepsilon \gamma^t
\end{align*}
$s_G$ is arbitrary so we conclude Equation \ref{eq:clm1Induct}. As $T \rightarrow \infty$, $\sum_{t=0}^{T-1} \varepsilon \gamma^t \rightarrow \frac{\varepsilon}{1-\gamma}$ by the sum of infinite geometric series and $Q_T \rightarrow Q_A$. Thus, Equation \ref{eq:clm1Induct} gives Claim \ref{clm:closeQs}.

@@

Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$ and its corresponding abstract state $s_A=\epQ(s_G)$.
Let $a^*_G$ stand for the optimal action in $s_G$, and $a^*_A$ stand for the optimal action in $s_A$:
\begin{align*}
a^*_G = \argmin Q_G(s_G, a), \hspace{4mm}
a^*_A = \argmin Q_A(s_A, a).
\end{align*}
The optimal action in the abstract MDP has a $Q$-value in the ground MDP that is nearly optimal:
\begin{equation}
\label{eq:Q*Claim2}
V_G(s_G) \leq Q_G(s_G, a^*_A) + \frac{2\varepsilon}{1-\gamma}.
\end{equation}
\end{clm}
By Claim~\ref{clm:closeQs},
\begin{align}
&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_A, a^*_G) + \frac{\varepsilon}{1-\gamma}.
\label{eq:Q*OptActionResult}
\end{align}
By the definition of $a^*_A$, we know that 
\begin{align}
Q_A(s_A, a^*_G) + \frac{\varepsilon}{1-\gamma} \leq Q_A(s_A, a^*_A) + \frac{\varepsilon}{1-\gamma}.
\end{align}
Lastly, again by Claim~\ref{clm:closeQs}, we know
\begin{align}
Q_A(s_A, a^*_A) + \frac{\varepsilon}{1-\gamma} \leq Q_G(s_g, a^*_A) + \frac{2\varepsilon}{1-\gamma}.
\end{align}
Therefore, Equation~\ref{eq:Q*Claim2} follows.
